### 2021-06-09 manuscript/manuscript.Rmd
add simulation script

---
title: "Untitled"
output: github_document
date: '`r format(Sys.time(), "%d %B, %Y")`'
bibliography: references.bib
knit: worcs::cite_all
---

```{r setup, include=FALSE}
library("worcs")
# We recommend that you prepare your raw data for analysis in 'prepare_data.R',
# and end that file with either open_data(yourdata), or closed_data(yourdata).
# Then, uncomment the line below to load the original or synthetic data
# (whichever is available), to allow anyone to reproduce your code:
# load_data()
knitr::opts_chunk$set(echo = TRUE)
```

This manuscript uses the Workflow for Open Reproducible Code in Science [@vanlissaWORCSWorkflowOpen2020] to ensure reproducibility and transparency. All code <!--and data--> are available at <git@github.com:cjvanlissa/moral_politics.git>.

This is an example of a non-essential citation [@@vanlissaWORCSWorkflowOpen2020]. If you change the rendering function to `worcs::cite_essential`, it will be removed.

<!--The function below inserts a notification if the manuscript is knit using synthetic data. Make sure to insert it after load_data().-->
`r notify_synthetic()`

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2021-06-09 simulated_data.R

@@ -1,0 +1,52 @@
+install.packages("lavaan")
+install.packages("BFpack")
+library(lavaan)
+library(BFpack)
+
+H1. Family values is positively associated with conservative-right orientation with an effect size of at least r = .1.  
+H2. Group loyalty is positively associated with conservative-right orientation with an effect size of at least r = .1.  
+H3. Reciprocity is positively associated with conservative-right orientation with an effect size of at least r = .1.
+H4. Heroism is positively associated with conservative-right orientation with an effect size of at least r = .1.
+H5. Deference is positively associated with conservative-right orientation with an effect size of at least r = .1.
+H6. Fairness is associated with progressive-left orientation with an effect size of at least r = .1. 
+H7. Property rights is positively associated with conservative-right orientation with an effect size of at least r = .1.
+
+
+
+mod_pop <- ' macfam =~ macfam1 + 0.8*macfam2 + 1.2*macfam3
+             macgrp =~ macgrp1 + 0.8*macgrp2 + 1.2*macgrp3
+             macrec =~ macrec1 + 0.8*macrec2 + 1.2*macrec3
+             macher =~ macher1 + 0.8*macher2 + 1.2*macher3
+             macdef =~ macdef1 + 0.8*macdef2 + 1.2*macdef3
+             macfai =~ macfai1 + 0.8*macfai2 + 1.2*macfai3
+             macpro =~ macpro1 + 0.8*macpro2 + 1.2*macpro3
+             macfam ~~ .12 * conservative
+             macgrp ~~ .1 * conservative
+             macrec ~~ .14 * conservative
+             macher ~~ .1 * conservative
+             macdef ~~ .16 * conservative
+             macfai ~~ -.2 * conservative
+             macpro ~~ .1 * conservative
+'
+
+# generate data
+set.seed(1234)
+df <- simulateData(mod_pop, sample.nobs=100L)
+
+# fit model
+mod <- gsub("\\d\\.\\d\\*", "", mod_pop)
+fit <- sem(mod, data=df)
+
+tab <- standardizedsolution(fit)
+keep_these <- which(tab$op == "~~" & tab$rhs == "conservative" & !tab$lhs == "conservative")
+estimates <- tab[keep_these, ]$est.std
+names(estimates) <- c("fam", "grp", "rec", "her", "def", "fai", "pro")
+
[…]

### 2021-06-11 cor_syntax_from_table.R
improve sim

@@ -1,0 +1,21 @@
+tmp <- read.table("clipboard", header = T)
+tmp <- tmp[8:14, grepl(".1", names(tmp), fixed = T)]
+rownames(tmp) <- colnames(tmp) <- c("fam", "grp", "rec", "her", "def", "fai", "pro")
+
+cors <- tmp[upper.tri(tmp)]
+cors <- expand.grid(colnames(tmp), rownames(tmp))
+cors$val <- paste0(" ~~ ", as.vector(as.matrix(t(tmp))), " * ")
+cors <- cors[, c(1,3,2)]
+cors <- matrix(apply(cors, 1, paste0, collapse = ""), ncol = 7, byrow = T)
+
+cors <- cors[upper.tri(cors)]
+cat(cors, sep = "\n")
+
+tmp <- readClipboard()
+tmp <- tmp[!tmp == ""]
+tmp <- paste0(paste0("mac", rep(c("fam", "grp", "rec", "her", "def", "fai", "pro"), each = 3)), 
+              " =~ ",
+              tmp,
+              "* ",
+              paste0("mac", rep(c("fam", "grp", "rec", "her", "def", "fai", "pro"), each = 3), 1:3))
+cat(tmp, sep = "\n")

### 2021-06-11 simulated_data.R

@@ -1,52 +1,274 @@
-install.packages("lavaan")
-install.packages("BFpack")
+#install.packages("lavaan")
+#install.packages("BFpack")
+#install.packages("Matrix")
+library(Matrix)
 library(lavaan)
 library(BFpack)
 
-H1. Family values is positively associated with conservative-right orientation with an effect size of at least r = .1.  
-H2. Group loyalty is positively associated with conservative-right orientation with an effect size of at least r = .1.  
-H3. Reciprocity is positively associated with conservative-right orientation with an effect size of at least r = .1.
-H4. Heroism is positively associated with conservative-right orientation with an effect size of at least r = .1.
-H5. Deference is positively associated with conservative-right orientation with an effect size of at least r = .1.
-H6. Fairness is associated with progressive-left orientation with an effect size of at least r = .1. 
-H7. Property rights is positively associated with conservative-right orientation with an effect size of at least r = .1.
+true_es <- .11
+sample_sizes <- c(us = 517, dk = 522, nl = 350)
+
+hypotheses <- lapply(c("fam", "grp", "rec", "her", "def", "fai", "pro"), function(x){
+  if(!x == "fai"){
+    paste0("(", paste0(grep(x, names(est), fixed = TRUE, value = TRUE), collapse = ", "), ") > .1")
+  } else {
+    paste0("(", paste0(grep(x, names(est), fixed = TRUE, value = TRUE), collapse = ", "), ") < -.1")
+  }
+})
+hypotheses[[8]] <- gsub("[<>]", "=", gsub("\\b(fam|grp)_(.+?)_", "\\2ON\\1_", gsub("\\) > 0 & \\(", ", ", paste0(gsub("-?\\.1", "0", hypotheses[[1]]), " & ", gsub(".1", "0", hypotheses[[2]], fixed = TRUE)))))
+hypotheses[[9]] <- gsub("fam", "rec", gsub("grp", "fai", hypotheses[[8]], fixed = TRUE), fixed = TRUE)
 
 
+pop_mod_mac <- ' 
+# Mac loadings
+fam =~ 0.765* fam1
[…]

### 2021-06-11 simulated_data.R
finalize sim

@@ -4,17 +4,20 @@
 library(Matrix)
 library(lavaan)
 library(BFpack)
+library(ggplot2)
 
-true_es <- .11
+sim_conditions <- lapply(c(0, .1, .2, .3), function(true_es){
+#true_es <- .2
 sample_sizes <- c(us = 517, dk = 522, nl = 350)
 
-hypotheses <- lapply(c("fam", "grp", "rec", "her", "def", "fai", "pro"), function(x){
-  if(!x == "fai"){
-    paste0("(", paste0(grep(x, names(est), fixed = TRUE, value = TRUE), collapse = ", "), ") > .1")
-  } else {
-    paste0("(", paste0(grep(x, names(est), fixed = TRUE, value = TRUE), collapse = ", "), ") < -.1")
-  }
-})
+hypotheses <- list("(fam_secs_us, fam_sic_us, fam_sepa_dk, fam_sic_dk, fam_secs_nl, fam_sepa_nl, fam_sic_nl) > .1",
+                   "(grp_secs_us, grp_sic_us, grp_sepa_dk, grp_sic_dk, grp_secs_nl, grp_sepa_nl, grp_sic_nl) > .1",
+                   "(rec_secs_us, rec_sic_us, rec_sepa_dk, rec_sic_dk, rec_secs_nl, rec_sepa_nl, rec_sic_nl) > .1",
+                   "(her_secs_us, her_sic_us, her_sepa_dk, her_sic_dk, her_secs_nl, her_sepa_nl, her_sic_nl) > .1",
+                   "(def_secs_us, def_sic_us, def_sepa_dk, def_sic_dk, def_secs_nl, def_sepa_nl, def_sic_nl) > .1",
+                   "(fai_secs_us, fai_sic_us, fai_sepa_dk, fai_sic_dk, fai_secs_nl, fai_sepa_nl, fai_sic_nl) < -.1",
+                   "(pro_secs_us, pro_sic_us, pro_sepa_dk, pro_sic_dk, pro_secs_nl, pro_sepa_nl, pro_sic_nl) > .1"
+                   )
 hypotheses[[8]] <- gsub("[<>]", "=", gsub("\\b(fam|grp)_(.+?)_", "\\2ON\\1_", gsub("\\) > 0 & \\(", ", ", paste0(gsub("-?\\.1", "0", hypotheses[[1]]), " & ", gsub(".1", "0", hypotheses[[2]], fixed = TRUE)))))
[…]

### 2021-11-09 analysis.R
Fix analysis script

@@ -1,23 +1,10 @@
-#install.packages("lavaan")
-#install.packages("BFpack")
-#install.packages("Matrix")
-library(Matrix)
+library(worcs)
 library(lavaan)
 library(BFpack)
 library(ggplot2)
-
-sim_conditions <- lapply(c(0, .1, .2, .3), function(true_es){
-#true_es <- .2
-sample_sizes <- c(us = 517, dk = 522, nl = 350)
-# Logic is as follows: Each conceptual hypothesis can be tested across several scales, across several samples.
-# For example, "fam" represents the correlation between family values and political orientation.
-# secs and sepa are three scales of political orientation.
-# us, dk, and nl are three countries in which data were collected.
-# Not every scale is available in each country.
-# Thus, the hypothesis "family values are correlated > .1 with political orientation" can be
-# evaluated on all of these parameters:
-# (fam_secs_us, fam_sepa_dk, fam_secs_nl, fam_sepa_nl)
- 
+library(tidySEM)
+set.seed(22)
+sample_sizes <- sapply(dat, nrow)
 hypotheses <- list("(fam_secs_soc_us, fam_secs_eco_us, fam_sepa_soc_dk, fam_sepa_eco_dk, fam_secs_soc_nl, fam_secs_eco_nl, fam_sepa_soc_nl, fam_sepa_eco_nl) > .1",
                    "(grp_secs_soc_us, grp_secs_eco_us, grp_sepa_soc_dk, grp_sepa_eco_dk, grp_secs_soc_nl, grp_secs_eco_nl, grp_sepa_soc_nl, grp_sepa_eco_nl) > .1",
                    "(rec_secs_soc_us, rec_secs_eco_us, rec_sepa_soc_dk, rec_sepa_eco_dk, rec_secs_soc_nl, rec_secs_eco_nl, rec_sepa_soc_nl, rec_sepa_eco_nl) > .1",
@@ -30,316 +17,131 @@ hypotheses[[8]] <- gsub("[<>]", "=", gsub("\\b(fam|grp)_((sepa|secs)_(soc|eco))_
 hypotheses[[9]] <- gsub("fam", "rec", gsub("grp", "fai", hypotheses[[8]], fixed = TRUE), fixed = TRUE)
 
 
-pop_mod_mac <- ' 
-# Mac loadings
-fam =~ 0.765* fam1
[…]

### 2021-11-09 scales_list.R

@@ -1,0 +1,83 @@
+scales_list <-
+  list(
+    dk = list(
+      sepa_soc = c("q9_1", "q9_2", "q9_3", "q9_4", "q9_5"),
+      sepa_eco = c("q10_1", "q10_2", "q10_3", "q10_4", "q10_5"),
+      fam = c("q5_1", "q5_8", "q5_15"),
+      grp = c("q5_2", "q5_9", "q5_16"),
+      rec = c("q5_3", "q5_10", "q5_17"),
+      her = c("q5_4", "q5_11", "q5_18"),
+      def = c("q5_5", "q5_12", "q5_19"),
+      fai = c("q5_6", "q5_13", "q5_20"),
+      pro = c("q5_7", "q5_14", "q5_21")
+    ),
+    us = list(
+      secs_soc = c("sec1", "sec3", "sec4", "sec7", "sec8", "sec11", "sec12"),
+      secs_eco = c("sec2", "sec5", "sec6", "sec9", "sec10"),
+      fam = c("mj1", "mj2", "mj3"),
+      grp = c("mj4", "mj5", "mj6"),
+      rec = c("mj7", "mj8", "mj9"),
+      her = c("mj10", "mj11", "mj12"),
+      def = c("mj13", "mj14", "mj15"),
+      fai = c("mj16", "mj17", "mj18"),
+      prop = c("mj19", "mj20", "mj21")
+    ),
+    nl = list(
+      sepa_soc = c("dsc_1", "dsc_2", "dsc_3", "dsc_4", "dsc_5"),
+      sepa_eco = c("silwrw_1", "silwrw_2", "silwrw_3", "silwrw_4", "silwrw_5"),
+      secs_soc = c("secs_1", "secs_3", "secs_4", "secs_7", "secs_8", "secs_11", "secs_12"),
+      secs_eco = c("secs_2", "secs_5", "secs_6", "secs_9", "secs_10"),
+      fam = c("mac_q_1j", "mac_q_8j", "mac_q_15j"),
+      grp = c("mac_q_2j", "mac_q_9j", "mac_q_16j"),
+      rec = c("mac_q_3j", "mac_q_10j", "mac_q_17j"),
+      her = c("mac_q_4j", "mac_q_11j", "mac_q_18j"),
+      def = c("mac_q_5j", "mac_q_12j", "mac_q_19j"),
+      fai = c("mac_q_6j", "mac_q_13j", "mac_q_20j"),
[…]

### 2021-11-09 codebook_nl.Rmd
first version of results

---
title: "Codebook created on 2021-11-05 at 2021-11-05 12:55:43"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, results = 'asis')
```

A codebook contains documentation and metadata describing the contents, structure, and layout of a data file.

## Dataset description
The data contains 401 cases and 43 variables.

## Codebook

```{r}
summaries <- read.csv("./codebook_nl.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

### Legend

* __Name__: Variable name
* __type__: Data type of the variable
* __missing__: Proportion of missing values for this variable
* __unique__: Number of unique values
* __mean__: Mean value
* __median__: Median value
* __mode__: Most common value (for categorical variables, this shows the frequency of the most common category)
* **mode_value**: For categorical variables, the value of the most common category
* __sd__: Standard deviation (measure of dispersion for numerical variables
* __v__: Agresti's V (measure of dispersion for categorical variables)
* __min__: Minimum value
* __max__: Maximum value
* __range__: Range between minimum and maximum value
* __skew__: Skewness of the variable
* __skew_2se__: Skewness of the variable divided by 2*SE of the skewness. If this is greater than abs(1), skewness is significant
* __kurt__: Kurtosis (peakedness) of the variable
* __kurt_2se__: Kurtosis of the variable divided by 2*SE of the kurtosis. If this is greater than abs(1), kurtosis is significant.

This codebook was generated using the [Workflow for Open Reproducible Code in Science (WORCS)](https://osf.io/zcvbs/)

### 2021-11-09 manuscript/manuscript.Rmd
first version of results

@@
 ---
-title: "Untitled"
-output: github_document
+title: "Morality, politics, and cooperation"
+output: bookdown::html_document2
 date: '`r format(Sys.time(), "%d %B, %Y")`'
@@
 ```{r setup, include=FALSE}
-library("worcs")
 # We recommend that you prepare your raw data for analysis in 'prepare_data.R',
@@
 # (whichever is available), to allow anyone to reproduce your code:
-# load_data()
-knitr::opts_chunk$set(echo = TRUE)
+library("worcs")
+knitr::opts_chunk$set(echo = FALSE, results = "hide", message = FALSE, warning = FALSE)
+options(knitr.kable.NA = '')
+library(ggplot2)
+library(tidySEM)
+library(lavaan)
+library(semTools)
+library(kableExtra)
+library(bookdown)
+library(psych)
+dat <- load_data(to_envir = FALSE)
+source("../scales_list.R")
+scales_list <- lapply(scales_list, function(i){
+  tmp <- lapply(names(i), function(j){ paste0(j, "_", 1:length(i[[j]]))})
+  names(tmp) <- names(i)
+  tmp
+  })
+set.seed(1)
+cfas <- lapply(names(scales_list), function(cnt){
+  results <- t(sapply(scales_list[[cnt]], function(scal){
+    out <- cfa(paste0("F =~ ", paste0(scal, collapse = "+")), std.lv = TRUE, data = dat[[cnt]])
+    paran <- fa.parallel(dat[[cnt]][, scal])
+    tab <- table_results(out, columns = NULL, digits=3)
+    tab <- tab[-nrow(tab), ]
+    loadns <- as.numeric(tab$est_std)[tab$op == "=~"]
+    r2s <- lavInspect(out, "r2")
+    omga <- semTools::reliability(out, what = "omega")[1,1]
+    c(Subscale = gsub("_\\d$", "", scal[1]),
+      Items = length(scal),
+      n = out@Data@nobs[[1]],
+      formatC(unlist(table_fit(out)[1, c("chisq", "cfi", "tli", "rmsea", "srmr")]), digits = 3, format = "f"), 
+      formatC(c(min_load = min(loadns), max_load = max(loadns), min_r2 = min(r2s), max_r2 = max(r2s), omega = omga), digits = 3, format = "f"),
+      Reliability = tidySEM:::interpret(omga),
+      Factors = fa.parallel(dat[[cnt]][,scal]) $nfact
+      )
+  }))
+})
+names(cfas) <- names(scales_list)
 ```
 
-This manuscript uses the Workflow for Open Reproducible Code in Science [@vanlissaWORCSWorkflowOpen2020] to ensure reproducibility and transparency.
-All code <!--and data--> are available at <git@github.com:cjvanlissa/moral_politics.git>.
+## Necessary deviations from preregistration
 
-This is an example of a non-essential citation [@@vanlissaWORCSWorkflowOpen2020]. If you change the rendering function to `worcs::cite_essential`, it will be removed.
+When attempting to conduct the preregistered analyses,
+we noticed that the model did not converge in one of the datasets (NL).
+We examined individual CFAs for the included scales to determine potential
+sources of misspecification.
+These analyses, summarized below, indicate that several scales in that dataset
+displayed evidence of not being unidimensional,
+had poor reliability, or had no factors with Eigenvalues greater than would be expected by random chance.
 
-<!--The function below inserts a notification if the manuscript is knit using synthetic data. Make sure to insert it after load_data().-->
-`r notify_synthetic()`
-
-## GitHub Documents
-
-This is an R Markdown format used for publishing markdown documents to GitHub.
-When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.
-
-## Including Code
-
-You can include R code in the document as follows:
-
-```{r cars}
-summary(cars)
+```{r tabscale, results = "asis"}
+invisible(lapply(names(cfas), function(cntr){
+  print({kbl(cfas[[cntr]], caption = paste0("Scale reliability ", cntr)) |>
+  kable_styling(bootstrap_options = c("striped", "hover"))
+})}))
 ```
 
-## Including Plots
+To understand these issues better, we performed exploratory factor analysis on scales that showed indications of being non-unidimensional in at least one country.
 
-You can also embed plots, for example:
+```{r notunidim, results = "asis"}
+allscales <- do.call(c, scales_list)
+nfacs <- as.integer(do.call(c, lapply(cfas, function(i){i[, 'Factors']})))
+check_these <- nfacs > 1
+these_scales <- unique(do.call(c, lapply(cfas, function(i){i[, 'Subscale']}))[check_these])
+check_these <- grep(paste0("^.{2}\\.(", paste0(these_scales, collapse = "|"), ")$"), names(allscales))
+these_scales <- allscales[check_these]
+nfacs <- nfacs[check_these]
+nfacs[nfacs == 0] <- 2
+out <- mapply(function(scal, nfac){
+  fa(dat[[substring(scal, first = 1, last = 2)]][these_scales[[scal]]], nfac)
+}, scal = names(these_scales), nfac = rep(2, length(these_scales)))
 
-```{r pressure, echo=FALSE}
-plot(pressure)
+these_scales <- unique(do.call(c, lapply(cfas, function(i){i[, 'Subscale']}))[check_these])
+for(scal in these_scales){
+  print(kbl(do.call(cbind,
+  lapply(grep(scal, names(out), value = TRUE), function(i){
+    tmp <- data.frame(unclass(out[[i]][["loadings"]]))
+    names(tmp) <- paste0(substring(i, 1,2), " Factor ", 1:ncol(tmp))
+    rownames(tmp) <- paste0("Item ", 1:nrow(tmp))
+    tmp
+  })
+), digits = 2, caption = paste0("Factor loadings for ", scal))|>
+  kable_styling(bootstrap_options = c("striped", "hover")))
+}
 ```
 
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
+These factor analyses suggest that items 3-5 of sepa_soc loaded most consistently on the same factor.
+Similarly, items 3-5 of sepa_eco loaded most consistently on the same factor.
+For secs_soc, only items 4-5 loaded consistently high on the same factor.
+For secs_eco, no items loaded consistently high on the same factor.
+We removed items not consistently loading on one factor,
+and dropped secs_eco entirely.
+
+```{r, include=FALSE}
+use_scales <- lapply(scales_list, function(i){
+  thenames <- grepl("sepa_(soc|eco)", names(i))
+  if(any(thenames)){
+    i[which(thenames)] <- lapply(i[which(thenames)], `[`, 3:5)
+  }
+  i
+})
+use_scales <- lapply(use_scales, function(i){
+  thenames <- grepl("secs_soc", names(i))
+  if(any(thenames)){
+    i[which(thenames)] <- lapply(i[which(thenames)], `[`, 4:5)
+  }
+  i
+})
+use_scales$us$secs_eco <- NULL
+use_scales$nl$secs_eco <- NULL
+
+set.seed(1)
+cfas <- lapply(names(use_scales), function(cnt){
+  results <- t(sapply(use_scales[[cnt]], function(scal){
+    out <- cfa(paste0("F =~ ", paste0(scal, collapse = "+")), std.lv = TRUE, data = dat[[cnt]])
+    paran <- fa.parallel(dat[[cnt]][, scal])
+    tab <- table_results(out, columns = NULL, digits=3)
+    tab <- tab[-nrow(tab), ]
+    loadns <- as.numeric(tab$est_std)[tab$op == "=~"]
+    r2s <- lavInspect(out, "r2")
+    omga <- semTools::reliability(out, what = "omega")[1,1]
+    c(Subscale = gsub("_\\d$", "", scal[1]),
+      Items = length(scal),
+      n = out@Data@nobs[[1]],
+      formatC(unlist(table_fit(out)[1, c("chisq", "cfi", "tli", "rmsea", "srmr")]), digits = 3, format = "f"), 
+      formatC(c(min_load = min(loadns), max_load = max(loadns), min_r2 = min(r2s), max_r2 = max(r2s), omega = omga), digits = 3, format = "f"),
+      Reliability = tidySEM:::interpret(omga),
+      Factors = invisible(fa.parallel(dat[[cnt]][,scal])$nfact)
+      )
+  }))
+})
+names(cfas) <- names(use_scales)
+
+meas_inv <- sapply(use_scales$dk, function(scal){
+  tmpdat <- rbind(tryCatch(cbind(dat$nl[, scal], Country = "NL"), error = function(e) NULL),
+                  tryCatch(cbind(dat$dk[, scal], Country = "DK"), error = function(e) NULL),
+                  tryCatch(cbind(dat$us[, scal], Country = "US"), error = function(e) NULL))
+  conf <- cfa(paste0("F =~ ", paste0(scal, collapse = "+")), std.lv = TRUE, data = tmpdat, group = "Country")
+  metr <- cfa(paste0("F =~ ", paste0(scal, collapse = "+")), std.lv = TRUE, data = tmpdat, group = "Country", group.equal = "loadings")
+  tst <- anova(conf, metr)
+  unlist(tst[2, c("Chisq diff", "Df diff", "Pr(>Chisq)")])
+})
+```
+
+```{r tabscaleuse, results = "asis"}
+invisible(lapply(names(cfas), function(cntr){
+  print({kbl(cfas[[cntr]], caption = paste0("Scale reliability ", cntr)) |>
+  kable_styling(bootstrap_options = c("striped", "hover"))
+})}))
+```
+
+We further examined measurement invariance across countries,
+and found that metric invariance did not hold for these scales: `r paste0(colnames(meas_inv)[meas_inv[3, ] < .05], collapse = ", ")`.
+This lack of measurement invariance must be taken into account when aggregating evidence across countries.
+
+```{r tabinvar, results = "asis"}
+meas_inv |>
+  kbl(caption = "Measurement invariance tests for the difference between a configural and metrically invariant model.", digits = 3) |>
+  kable_styling(bootstrap_options = c("striped", "hover"))
+```
+
+## Planned analyses
+
+```{r, code=xfun::read_utf8('../analysis.R')}
+
+```
+
+```{r tabresults, results = "asis"}
+interpret_bf <- function(bf){
+  sapply(bf, function(bf){
+    if(bf < 1/10) return("rejected")
+    if(bf < 1/3) return("rejected")
+    if(bf >= 1/3 & bf <= 3) return("inconclusive")
+    if(bf > 3 & bf <= 10) return("supported")
+  return("supported")
+  })
+}
+invisible(lapply(1:length(bayesfactors), function(h){
+  print({
+    kbl(est_for_hyp[[h]], caption = paste0("Parameters used to test hypothesis ", h, ".
+Evidence in favor of the hypothesis: BF = ", formatC(bayesfactors[h], digits = 3, format = "f"), " (", interpret_bf(bayesfactors[h]), ")."), digits = 3) |>
+  kable_styling(bootstrap_options = c("striped", "hover"))
+})}))
+```
+
+According to these analyses, hypotheses `r paste0(which(bayesfactors > 3), collapse = ", ")` were supported.
+
+These results are qualified by the relatively poor psychometric properties of some scales,
+and the poor model fit of the CFA estimated in the three countries (see below).
+Inspection of the modification indices suggested that adding cross-loadings might improve model fit,
+but with the low number of indicators per factor this might compromise interpretability.
+A likely explanation for the relatively poor model fit is the low explained variance in some items (see Table 3).
+
+```{r tabfits, results = "asis"}
+fit_17 <- t(sapply(res_list17, fitmeasures))
+fit_17 <- fit_17[, c("npar", "chisq", "df", "cfi", "tli", "rmsea", "srmr")]
+kbl(fit_17, caption = paste0("Fit of models used to test hypotheses 1-7."), digits = 3) |>
+  kable_styling(bootstrap_options = c("striped", "hover"))
+```

### 2021-11-09 model.r

@@ -1,0 +1,197 @@
+list(us = " 
+fam ~~ secs_soc
+grp ~~ secs_soc
+rec ~~ secs_soc
+her ~~ secs_soc
+def ~~ secs_soc
+fai ~~ secs_soc
+pro ~~ secs_soc
+
+fam ~~ secs_eco
+grp ~~ secs_eco
+rec ~~ secs_eco
+her ~~ secs_eco
+def ~~ secs_eco
+fai ~~ secs_eco
+pro ~~ secs_eco
+",
+dk = "
+# Mac loadings
+fam =~ fam1
+fam =~ fam2
+fam =~ fam3
+grp =~ grp1
+grp =~ grp2
+grp =~ grp3
+rec =~ rec1
+rec =~ rec2
+rec =~ rec3
+her =~ her1
+her =~ her2
+her =~ her3
+def =~ def1
+def =~ def2
+def =~ def3
+fai =~ fai1
+fai =~ fai2
+fai =~ fai3
+pro =~ pro1
+pro =~ pro2
+pro =~ pro3
+
+# Mac cors
+grp ~~ fam
+rec ~~ fam
+rec ~~ grp
+her ~~ fam
+her ~~ grp
+her ~~ rec
+def ~~ fam
+def ~~ grp
+def ~~ rec
+def ~~ her
+fai ~~ fam
+fai ~~ grp
+fai ~~ rec
+fai ~~ her
+fai ~~ def
+pro ~~ fam
+pro ~~ grp
+pro ~~ rec
+pro ~~ her
+pro ~~ def
+pro ~~ fai
+# Social and economic policy attitudes
+sepa_soc =~ sepa1
+sepa_soc =~ sepa2
+sepa_soc =~ sepa3
+sepa_soc =~ sepa4
+sepa_soc =~ sepa5
+sepa_eco =~ sepa6
+sepa_eco =~ sepa7
+sepa_eco =~ sepa8
+sepa_eco =~ sepa9
+sepa_eco =~ sepa10
+
+# Cors with Social and economic policy attitudes
+fam ~~ sepa_soc
+grp ~~ sepa_soc
+rec ~~ sepa_soc
+her ~~ sepa_soc
+def ~~ sepa_soc
+fai ~~ sepa_soc
+pro ~~ sepa_soc
+
+fam ~~ sepa_eco
+grp ~~ sepa_eco
+rec ~~ sepa_eco
+her ~~ sepa_eco
+def ~~ sepa_eco
[…]

### 2021-11-09 prepare_data.R

@@ -4,3 +4,44 @@
 # to store the data.
 
 library(worcs)
+library(foreign)
+library(haven)
+source("scales_list.r")
+nl <- read.spss("nl.sav", to.data.frame = TRUE, use.value.labels = TRUE)
+names(nl) <- tolower(names(nl))
+all(unlist(scales_list$nl) %in% names(nl))
+unlist(scales_list$nl)[!(unlist(scales_list$nl) %in% names(nl))]
+nl <- nl[unlist(scales_list$nl)]
+# Rescale variables, because otherwise the observed covariances for some
+# variables will be a factor 1000 larger than for others. This complicates model
+# convergence.
+desc <- descriptives(nl)
+rescale_these <- desc$name[which(desc$max > 90)]
+nl[,rescale_these] <- nl[, rescale_these]/10
+names(nl) <- unlist(lapply(names(scales_list$nl), function(nam){paste0(nam, "_", 1:length(scales_list$nl[[nam]]))}))
+nl[sapply(nl, inherits, what = "factor")] <- lapply(nl[sapply(nl, inherits, what = "factor")], as.numeric)
+rev_these <- which(unlist(reverse_coded[["nl"]]))
+maxval <- sapply(nl[rev_these], max, na.rm = TRUE) + 1
+nl[rev_these] <- mapply(function(c, vec){c-vec}, c = maxval, vec = nl[rev_these])
+closed_data(nl, synthetic = FALSE)
+
+dk <- read_dta("dk.dta")
+names(dk) <- tolower(names(dk))
+all(unlist(scales_list$dk) %in% names(dk))
+dk <- dk[unlist(scales_list$dk)]
+names(dk) <- unlist(lapply(names(scales_list$dk), function(nam){paste0(nam, "_", 1:length(scales_list$dk[[nam]]))}))
+rev_these <- which(unlist(reverse_coded[["dk"]]))
+maxval <- sapply(dk[rev_these], max, na.rm = TRUE) + 1
+dk[rev_these] <- mapply(function(c, vec){c-vec}, c = maxval, vec = dk[rev_these])
+closed_data(dk, synthetic = FALSE)
+
+us <- read.csv("us_original.csv", stringsAsFactors = FALSE, skip = 2, header = FALSE)
+names_us <- read.csv("us_original.csv", stringsAsFactors = FALSE)
+names(us) <- tolower(names(names_us))
+all(unlist(scales_list$us) %in% names(us))
[…]

### 2021-11-09 scales_list.R

@@ -20,7 +20,7 @@ scales_list <-
       her = c("mj10", "mj11", "mj12"),
       def = c("mj13", "mj14", "mj15"),
       fai = c("mj16", "mj17", "mj18"),
-      prop = c("mj19", "mj20", "mj21")
+      pro = c("mj19", "mj20", "mj21")
     ),
     nl = list(
       sepa_soc = c("dsc_1", "dsc_2", "dsc_3", "dsc_4", "dsc_5"),

### 2021-11-09 manuscript/manuscript.Rmd
minor improvements to writing

@@
 When attempting to conduct the preregistered analyses,
-we noticed that the model did not converge in one of the datasets (NL).
+the model did not converge in one of the datasets (NL).
 We examined individual CFAs for the included scales to determine potential
 sources of misspecification.
-These analyses, summarized below, indicate that several scales in that dataset
-displayed evidence of not being unidimensional,
-had poor reliability, or had no factors with Eigenvalues greater than would be expected by random chance.
+These analyses, summarized below, indicated that several scales in that dataset
+displayed evidence of not being unidimensional or had no factors with Eigenvalues greater than would be expected by random chance (see column 'Factors', which is based on Horn's parallel analysis, 1965),
+had poor reliability (estimated using McDonald's Omega, which is calculated from the factor loadings and does not assume that all factor loadings are identical as Cronbach's alpha does).
 
@@
 and dropped secs_eco entirely.
+We applied these changes consistently across countries.
 
@@
 These results are qualified by the relatively poor psychometric properties of some scales,
+the lack of measurement invariance for some scales,
 and the poor model fit of the CFA estimated in the three countries (see below).

### 2021-11-10 codebook_tris.Rmd
add tris' data for exploratory analysis

--- 2021-11-09 codebook_nl.Rmd
@@
 ---
-title: "Codebook created on 2021-11-05 at 2021-11-05 12:55:43"
+title: "Codebook created on 2021-11-10 at 2021-11-10 14:59:00"
 output: github_document
@@
 ## Dataset description
-The data contains 401 cases and 43 variables.
+The data contains 1337 cases and 33 variables.
 
@@
 ```{r}
-summaries <- read.csv("./codebook_nl.csv", stringsAsFactors = FALSE)
+summaries <- read.csv("./codebook_tris.csv", stringsAsFactors = FALSE)
 summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]

### 2021-11-10 analysis_tris.R

@@ -1,0 +1,147 @@
+library(worcs)
+library(lavaan)
+library(BFpack)
+library(ggplot2)
+library(tidySEM)
+set.seed(22)
+sample_sizes <- sapply(dat, nrow)
+hypotheses <- list("(fam_secs_soc_us, fam_secs_eco_us, fam_sepa_soc_dk, fam_sepa_eco_dk, fam_secs_soc_nl, fam_secs_eco_nl, fam_sepa_soc_nl, fam_sepa_eco_nl) > .1",
+                   "(grp_secs_soc_us, grp_secs_eco_us, grp_sepa_soc_dk, grp_sepa_eco_dk, grp_secs_soc_nl, grp_secs_eco_nl, grp_sepa_soc_nl, grp_sepa_eco_nl) > .1",
+                   "(rec_secs_soc_us, rec_secs_eco_us, rec_sepa_soc_dk, rec_sepa_eco_dk, rec_secs_soc_nl, rec_secs_eco_nl, rec_sepa_soc_nl, rec_sepa_eco_nl) > .1",
+                   "(her_secs_soc_us, her_secs_eco_us, her_sepa_soc_dk, her_sepa_eco_dk, her_secs_soc_nl, her_secs_eco_nl, her_sepa_soc_nl, her_sepa_eco_nl) > .1",
+                   "(def_secs_soc_us, def_secs_eco_us, def_sepa_soc_dk, def_sepa_eco_dk, def_secs_soc_nl, def_secs_eco_nl, def_sepa_soc_nl, def_sepa_eco_nl) > .1",
+                   "(fai_secs_soc_us, fai_secs_eco_us, fai_sepa_soc_dk, fai_sepa_eco_dk, fai_secs_soc_nl, fai_secs_eco_nl, fai_sepa_soc_nl, fai_sepa_eco_nl) < -.1",
+                   "(pro_secs_soc_us, pro_secs_eco_us, pro_sepa_soc_dk, pro_sepa_eco_dk, pro_secs_soc_nl, pro_secs_eco_nl, pro_sepa_soc_nl, pro_sepa_eco_nl) > .1"
+)
[…]

### 2021-11-10 prepare_data.R

@@ -45,3 +45,26 @@ rev_these <- which(unlist(reverse_coded[["us"]]))
 maxval <- sapply(us[rev_these], max, na.rm = TRUE) + 1
 us[rev_these] <- mapply(function(c, vec){c-vec}, c = maxval, vec = us[rev_these])
 closed_data(us, synthetic = FALSE)
+
+
+tris <- read.csv("aita_mac_secs 16.06.csv", stringsAsFactors = FALSE)
+names(tris) <- tolower(names(tris))
+
+scales_tris <- c(list(
+  secs_soc = c("secs_abortion", 
+               "secs_security", "secs_religion", "secs_marriage", 
+               "secs_traditionalvalues", "secs_familyunit", 
+               "secs_patriotism"),
+  secs_eco = c("secs_limitedgovernment", "secs_welfare", "secs_gun", "secs_fiscal", "secs_business")),
+  lapply(unique(cut(1:21, 7)), function(i) grep("^mac", names(tris), value = T)[which(cut(1:21, 7) == i)])
+)
+names(scales_tris)[-c(1:2)] <- names(scales_list$dk[-c(1:2)])
+
+tris <- tris[unlist(scales_tris)]
+
+rev_these <- c("secs_abortion", "secs_welfare")
+maxval <- sapply(tris[rev_these], max, na.rm = TRUE) + 1
+tris[rev_these] <- mapply(function(c, vec){c-vec}, c = maxval, vec = tris[rev_these])
+
+names(tris) <- unlist(lapply(names(scales_tris), function(i){paste0(i, "_", 1:length(scales_tris[[i]]))}))
+closed_data(tris, synthetic = FALSE)

### 2021-11-11 manuscript/manuscript.Rmd
finish tris analyses

@@
 title: "Morality, politics, and cooperation"
-output: bookdown::html_document2
+output:
+  bookdown::html_document2:
+    keep_md: yes
 date: '`r format(Sys.time(), "%d %B, %Y")`'
@@
 library(psych)
-dat <- load_data(to_envir = FALSE)
+dat <- load_data(to_envir = FALSE)[1:3]
 source("../scales_list.R")
@@
 ```
+
+# Exploratory analyses
+
+The preceding analyses were conceptually replicated in a fourth sample.
+Note that this sample used moral relevance scales instead of moral judgment scales.
+
+```{r, include = FALSE, code=xfun::read_utf8('../analysis_tris.R')}
+
+```
+
+This replication offered no support for any hypothesis except H`r which(bayesfactors_tris > 3)`:
+
+```{r, results = "asis"}
+trisfit <- unlist(table_fit(res_tris)[1, c("chisq", "cfi", "tli", "rmsea", "srmr")])
+for(i in 1:length(bayesfactors_tris)){
+  cat(
+    "* $BF_{h", i, "} = ", formatC(bayesfactors_tris[i], digits = 3, format = "f"),
+    "$, based on parameters ", 
+    paste0(names(est_for_hyp_tris[[i]]), " (", formatC(est_for_hyp_tris[[i]], digits = 3, format = "f"), ")", collapse = ", "), ".  \r\n",
+    sep = ""
+  )
+}
+```
+
+The fit of this model was also poor, though somewhat better than for the confirmatory analyses; `r paste0(names(trisfit), " = ", formatC(trisfit, digits = 3, format = "f"), collapse = ", ")`.

### 2021-11-11 analysis_tris.R

@@ -3,145 +3,220 @@ library(lavaan)
 library(BFpack)
 library(ggplot2)
 library(tidySEM)
-set.seed(22)
-sample_sizes <- sapply(dat, nrow)
-hypotheses <- list("(fam_secs_soc_us, fam_secs_eco_us, fam_sepa_soc_dk, fam_sepa_eco_dk, fam_secs_soc_nl, fam_secs_eco_nl, fam_sepa_soc_nl, fam_sepa_eco_nl) > .1",
-                   "(grp_secs_soc_us, grp_secs_eco_us, grp_sepa_soc_dk, grp_sepa_eco_dk, grp_secs_soc_nl, grp_secs_eco_nl, grp_sepa_soc_nl, grp_sepa_eco_nl) > .1",
-                   "(rec_secs_soc_us, rec_secs_eco_us, rec_sepa_soc_dk, rec_sepa_eco_dk, rec_secs_soc_nl, rec_secs_eco_nl, rec_sepa_soc_nl, rec_sepa_eco_nl) > .1",
-                   "(her_secs_soc_us, her_secs_eco_us, her_sepa_soc_dk, her_sepa_eco_dk, her_secs_soc_nl, her_secs_eco_nl, her_sepa_soc_nl, her_sepa_eco_nl) > .1",
-                   "(def_secs_soc_us, def_secs_eco_us, def_sepa_soc_dk, def_sepa_eco_dk, def_secs_soc_nl, def_secs_eco_nl, def_sepa_soc_nl, def_sepa_eco_nl) > .1",
-                   "(fai_secs_soc_us, fai_secs_eco_us, fai_sepa_soc_dk, fai_sepa_eco_dk, fai_secs_soc_nl, fai_secs_eco_nl, fai_sepa_soc_nl, fai_sepa_eco_nl) < -.1",
-                   "(pro_secs_soc_us, pro_secs_eco_us, pro_sepa_soc_dk, pro_sepa_eco_dk, pro_secs_soc_nl, pro_secs_eco_nl, pro_sepa_soc_nl, pro_sepa_eco_nl) > .1"
-)
[…]

### 2021-11-21 codebooks/codebook_dk.Rmd
initial commit
organizing code to orient myself in topic

--- 2021-11-09 codebook_nl.Rmd
@@
 ---
-title: "Codebook created on 2021-11-05 at 2021-11-05 12:55:43"
+title: "Codebook created on 2021-11-05 at 2021-11-05 12:56:18"
 output: github_document
@@
 ## Dataset description
-The data contains 401 cases and 43 variables.
+The data contains 552 cases and 31 variables.
 
@@
 ```{r}
-summaries <- read.csv("./codebook_nl.csv", stringsAsFactors = FALSE)
+summaries <- read.csv("./codebook_dk.csv", stringsAsFactors = FALSE)
 summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]

### 2021-11-21 analysis.R

@@ -4,7 +4,7 @@ library(BFpack)
 library(ggplot2)
 library(tidySEM)
 set.seed(22)
-sample_sizes <- sapply(dat, nrow)
+sample_sizes <- sapply(dat, nrow) #obtain sample sizes per country
 hypotheses <- list("(fam_secs_soc_us, fam_secs_eco_us, fam_sepa_soc_dk, fam_sepa_eco_dk, fam_secs_soc_nl, fam_secs_eco_nl, fam_sepa_soc_nl, fam_sepa_eco_nl) > .1",
                    "(grp_secs_soc_us, grp_secs_eco_us, grp_sepa_soc_dk, grp_sepa_eco_dk, grp_secs_soc_nl, grp_secs_eco_nl, grp_sepa_soc_nl, grp_sepa_eco_nl) > .1",
                    "(rec_secs_soc_us, rec_secs_eco_us, rec_sepa_soc_dk, rec_sepa_eco_dk, rec_secs_soc_nl, rec_secs_eco_nl, rec_sepa_soc_nl, rec_sepa_eco_nl) > .1",
@@ -13,8 +13,6 @@ hypotheses <- list("(fam_secs_soc_us, fam_secs_eco_us, fam_sepa_soc_dk, fam_sepa
                    "(fai_secs_soc_us, fai_secs_eco_us, fai_sepa_soc_dk, fai_sepa_eco_dk, fai_secs_soc_nl, fai_secs_eco_nl, fai_sepa_soc_nl, fai_sepa_eco_nl) < -.1",
                    "(pro_secs_soc_us, pro_secs_eco_us, pro_sepa_soc_dk, pro_sepa_eco_dk, pro_secs_soc_nl, pro_secs_eco_nl, pro_sepa_soc_nl, pro_sepa_eco_nl) > .1"
                    )
-hypotheses[[8]] <- gsub("[<>]", "=", gsub("\\b(fam|grp)_((sepa|secs)_(soc|eco))_", "\\2ON\\1_", gsub("\\) > 0 & \\(", ", ", paste0(gsub("-?\\.1", "0", hypotheses[[1]]), " & ", gsub(".1", "0", hypotheses[[2]], fixed = TRUE)))))
-hypotheses[[9]] <- gsub("fam", "rec", gsub("grp", "fai", hypotheses[[8]], fixed = TRUE), fixed = TRUE)
 
 
 mods_cor <- lapply(names(dat), function(country){
[…]

### 2021-11-21 simulated_data.R

@@ -26,9 +26,6 @@ hypotheses <- list("(fam_secs_soc_us, fam_secs_eco_us, fam_sepa_soc_dk, fam_sepa
                    "(fai_secs_soc_us, fai_secs_eco_us, fai_sepa_soc_dk, fai_sepa_eco_dk, fai_secs_soc_nl, fai_secs_eco_nl, fai_sepa_soc_nl, fai_sepa_eco_nl) < -.1",
                    "(pro_secs_soc_us, pro_secs_eco_us, pro_sepa_soc_dk, pro_sepa_eco_dk, pro_secs_soc_nl, pro_secs_eco_nl, pro_sepa_soc_nl, pro_sepa_eco_nl) > .1"
                    )
-hypotheses[[8]] <- gsub("[<>]", "=", gsub("\\b(fam|grp)_((sepa|secs)_(soc|eco))_", "\\2ON\\1_", gsub("\\) > 0 & \\(", ", ", paste0(gsub("-?\\.1", "0", hypotheses[[1]]), " & ", gsub(".1", "0", hypotheses[[2]], fixed = TRUE)))))
-hypotheses[[9]] <- gsub("fam", "rec", gsub("grp", "fai", hypotheses[[8]], fixed = TRUE), fixed = TRUE)
-
 
 pop_mod_mac <- ' 
 # Mac loadings
@@ -174,19 +171,11 @@ pro ~~ .1 * sepa_eco
 pop_mods <- lapply(list(us = pop_mod_us,
                         dk = pop_mod_dk,
                         nl = pop_mod_nl), function(x){
-                          gsub(".1 ", true_es, x, fixed = TRUE)
+                          gsub(".1 ", true_es, x, fixed = TRUE) #replace effect size .1 with true_es
                         })
 
 mods_cor <- lapply(pop_mods, gsub, pattern = "[0-9\\. -]{2,}\\s?\\*", replacement = "")
-mods_8 <- lapply(mods_cor, function(x){
-  x <- strsplit(x, split = "\\n")[[1]]
-  x <- x[!grepl("(rec|her|def|fai|pro)", x)]
-  x <- x[!grepl("#", x, fixed = TRUE)]
-  gsub("^(fam|grp) ~~ (secs|sepa)_(soc|eco)$", "\\2_\\3 ~ \\1", x)
-})
-mods_9 <- lapply(mods_8, function(x){
[…]

### 2021-12-14 Sim_Eli/Eli_vraag.R
Add Eli_Vraag

@@ -1,0 +1,138 @@
+dependencies <- c('MASS', 'bain')
+lapply(dependencies, function(x){library(x, character.only = T)})
+
+# rm(list=ls(all.names = T))
+# cat("\014")
+source('./Sim_Eli/smdata.R')
+
+
+#fix conditions for testing purposes
+var_n <- 3       # number of predictors
+n <- 100         # sample size per group
+hyp_val <- 0.1   # hypothesis threshold
+es <- 0.1        # true effect size
+k <- 10          # number of groups
+#tau2 <- 0       # variance of outcome variable
+
+#simulate data for every group
+dfs <- lapply(1:k, function(i){
+  simdata(es, var_n, n) 
+})
+
+#obtain estimates for correlations and their standard errors
+res <- lapply(dfs, function(x){
+  r <- cor(x) #obtain correlation matrix for df
+  ests <- r[,1][-1] #estimates
+  df <- nrow(x) - (var_n + 1) #degrees of freedom
+  se_ests <- sqrt((1 - ests^2)/df) #standard error sqrt((1-r^2)/df)
+  return(cbind(ests,se_ests))
+})
+names(res) <- paste0('group', 1:k)
+
+#prepare for bain() to obtain individual Bayes Factors
+res.i <- lapply(res, function(x){
+  ests <- x[,1] #extract estimate
+  sig <- diag(x[,2]) #extract varcov matrix
+  names(ests) <- paste0("r", 1:length(ests)) 
+  return(list(est = ests, sig = sig))
+})
+names(res.i) <- paste0("group", 1:k)
+
+#we could also use lm() instead of cor()
+# res <- lapply(dfs, function(x){
+#   fit.lin <- lm(y ~ .,data = as.data.frame(x))
+#   return(fit.lin)
+# })
+# names(res) <- paste0('group', 1:k)
+# 
+# #obtain for each group and every correlation the bayes factor
+# bf_individual <- lapply(res, function(x){
+#   bf <- bain(x, paste(paste0(sprintf("X%02d", 1:var_n), ">", hyp_val), collapse = '&'))
+#   #names(bf) <- paste0(names(ests))
+#   return(bf)
+# })
+
+
+#obtain for each group and every correlation the bayes factor
+bf_individual <- lapply(res.i, function(x){ #for all groups
+  ests <- x[['est']]                        #extract estimate
+  sig <- x[['sig']]                         #extract varcov matrix
[…]

### 2021-12-14 Sim_Eli/Simulatie_Eli.R

@@ -102,7 +102,9 @@ for(i in 1:length(res)){
   res.t <- cbind(res.t,res[[i]][,1]) #matrix with correlations in rows, groups in columns
   sigs <- cbind(sigs, res[[i]][,2]) #matrix with se's in rows, groups in columns
 }
-colnames(res.t) <- paste0("group", 1:k) #for clarity give names
+colnames(res.t) <- paste0("group", 1:k) 
+colnames(sigs) <- paste0("group", 1:k) 
+
 
 hyps <- paste0("(", paste0(colnames(res.t), collapse = ", "), ") > ", hyp_val)
 
@@ -225,11 +227,11 @@ BFs <- function(es, var_n, n, hyp_val, k){
 
 #specify hyperparameters
 HyperPar <- list(
-  es = c(0, 0.2, 0.4), #true effect size = true correlation with outcome
+  es = c(0, 0.1, 0.2), #true effect size = true correlation with outcome
   #tau2 = c(0, 0.1, 0.3), #reliability of measurement
-  n = c(200), #sample size (can be divided by I to obtain different sample sizes per group )
-  k = c(5, 10), #number of groups
-  hyp_val = c(0.2), #thresholds for informative hypotheses
+  n = c(300), #sample size (can be divided by I to obtain different sample sizes per group )
+  k = c(10), #number of groups
+  hyp_val = c(0, 0.1, 0.2), #thresholds for informative hypotheses
   #hyp_n = c(5,6,7) #number of hypotheses
   var_n = c(3) #numer of predictors
 )
@@ -246,7 +248,6 @@ results <- apply(conditions, 1, function(x){
 })
 names(results) <- sprintf("sim%02d", 1:length(results))
 saveRDS(results, file = "./Sim_Eli/results_Eli2.RData")
-
 
 
 

### 2021-12-14 Sim_Eli/smdata.R

@@ -1,12 +1,11 @@
 #simulate data function
 simdata <- function(es,var_n, n){
-  var_n <- var_n + 1 #to include outcome variable in mvrnorm()
-  M <- rep(0,var_n) #set mean to 0 for identification
+  var_n <- var_n + 1     #to include outcome variable in mvrnorm()
+  M <- rep(0,var_n)      #set mean to 0 for identification
   
-  # 1 can be replaced with some value for the desired variance of the outcome and predictors.
-  S <- diag(var_n) * 1 #predictors have variances of 1
-  #diag(S)[-1] <- tau2 #something like this could add some more noise to the predictors
-  #diag(S)[1] <- tau2 #add more noise to outcome measurement
+  S <- diag(var_n) * 1   #set initial variances to 1
+  #diag(S)[-1] <- tau2   #add extra variance to predictors
+  #diag(S)[1] <- tau2    #add extra noise to outcome measurement
   
   #this now sets all covariances s_y, s_xi to the same value. we can add some variability in the covariances
   S[,1][-1] <- es #covariances with outcome variable 
@@ -15,6 +14,8 @@ simdata <- function(es,var_n, n){
   colnames(df) <- c('y', sprintf("X%02d", 1:(var_n-1))) #give names
   return(df)
 }
+
+
 
 #product BF
 gPBF <- function(BFs){

### 2021-12-16 codebooks/codebook_us.Rmd

--- 2021-11-21 codebooks/codebook_dk.Rmd
@@
 ---
-title: "Codebook created on 2021-11-05 at 2021-11-05 12:56:18"
+title: "Codebook created on 2021-11-05 at 2021-11-05 13:07:36"
 output: github_document
@@
 ## Dataset description
-The data contains 552 cases and 31 variables.
+The data contains 518 cases and 33 variables.
 
@@
 ```{r}
-summaries <- read.csv("./codebook_dk.csv", stringsAsFactors = FALSE)
+summaries <- read.csv("./codebook_us.csv", stringsAsFactors = FALSE)
 summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]

### 2021-12-16 Sim_Eli/Eli_vraag.R
Update Eli_vraag.R

@@ -82,7 +82,6 @@ for(i in 1:k){
 results_i <- gPBF(BFs)
 results_i$GPBF 
 
-
 #prepare for BF_together; (group1_rj, group2_rj, ...,  groupk_rj) > hyp_val
 res.t <- sigs <- c() 
 for(i in 1:length(res)){
@@ -121,18 +120,24 @@ print(results)
 results <- readRDS("./Sim_Eli/results_Eli2.RData")
 results[[2]] #this is what the output for 1 simulation is.
 
-#Question:
-#The goal of the simulation is to test whether the product Bayes Factor works. 
-#We do so by taking the pBF over the individual BFs and check if it comes close to the true BF
-
-# 1.) How to calculate the true BF to compare the pBF against?
-
-# 2.) What is the added value of BF_together? 
-#     I understand that this checks if group1_r & group2_r & ... & groupk_r > hyp_val. And I see that
-#     as the number of groups increases to evaluate a parameter on, the less likely it becomes that 
-#     the parameter for all groups > hyp.val. 
-#     Does it serve as a benchmark to compare pBF against?
+# pop_effect <- ifelse(es >= hyp_val, 1, 0)
+# if(pop_effect == 1 & BF < 3){
+#   performance <- 0
+# } else if(pop_effect == 1 & BF > 3){
+#   performance <- 1
+# } else if(... etc)
 
 
 
+# Simuleer blok condities en simuleer data voor elke conditie.
+# Elk algoritme produceert een BFic en BFiu (output)
+# - (algoritmes staan o.a. in analysis.R en zijn bv prod(BF_individual), BF_together, gPBF))
+# We checken dus Hi tegen zowel Hc als Hu
+# De condities (en de daaruit volgende data) vertellen of de hypothese wel of niet kloppen.
+# Als de hypothese klopt, dan heeft het algoritme het goed gedaan als hij BF > 3 produceert. 
+# ALs de hypothese niet klopt, dan moet BF < 3.
+
+# BF_together lijkt afhankelijk van het aantal groepen. (misschien manier vinden om daarvoor te corrigeren zoals geometric mean ipv arithmetic mean.)
+# Andreas Brandmeijer = computer scientist die ook veel statistiek doet. Mail Caspar als je met hem wil praten
+# Caspar heeft Pema aangepast, goed om te bekijken
 

### 2021-12-16 manuscript/manuscript.Rmd
just omit the scale that prevents convergence. add meta-analysis

@@
 library("worcs")
+run_everything = FALSE
 knitr::opts_chunk$set(echo = FALSE, results = "hide", message = FALSE, warning = FALSE)
@@
 library(psych)
+library(knitr)
 dat <- load_data(to_envir = FALSE)[1:3]
@@
   })
+```
+
+```{r cfas, eval = run_everything}
 set.seed(1)
@@
 names(cfas) <- names(scales_list)
+saveRDS(cfas, "cfas.RData")
+```
+```{r}
+cfas <- readRDS("cfas.RData")
 ```
@@
 sources of misspecification.
-These analyses, summarized below, indicated that several scales in that dataset
-displayed evidence of not being unidimensional or had no factors with Eigenvalues greater than would be expected by random chance (see column 'Factors', which is based on Horn's parallel analysis, 1965),
-had poor reliability (estimated using McDonald's Omega, which is calculated from the factor loadings and does not assume that all factor loadings are identical as Cronbach's alpha does).
+These analyses indicated that the scale `secs_eco` in that dataset
+had no factors with Eigenvalues greater than would be expected by random chance (see column 'Factors', which is based on Horn's parallel analysis, 1965),
+and had poor reliability (estimated using McDonald's Omega, which is calculated from the factor loadings and does not assume that all factor loadings are identical as Cronbach's alpha does).
+After deleting this scale, the CFA model converged.
+It was therefore deemed necessary to remove this scale.
 
@@
 
-To understand these issues better, we performed exploratory factor analysis on scales that showed indications of being non-unidimensional in at least one country.
+<!-- To understand these issues better, we performed exploratory factor analysis on scales that showed indications of being non-unidimensional in at least one country. -->
 
-```{r notunidim, results = "asis"}
+```{r notunidim, results = "asis", include = FALSE}
 allscales <- do.call(c, scales_list)
@@
 
-These factor analyses suggest that items 3-5 of sepa_soc loaded most consistently on the same factor.
-Similarly, items 3-5 of sepa_eco loaded most consistently on the same factor.
-For secs_soc, only items 4-5 loaded consistently high on the same factor.
-For secs_eco, no items loaded consistently high on the same factor.
-We removed items not consistently loading on one factor,
-and dropped secs_eco entirely.
-We applied these changes consistently across countries.
+<!-- These factor analyses suggest that items 3-5 of sepa_soc loaded most consistently on the same factor. -->
+<!-- Similarly, items 1-3 of sepa_eco loaded most consistently on the same factor. -->
+<!-- For secs_soc, only items 4-5 loaded consistently high on the same factor. -->
+<!-- For secs_eco, no items loaded consistently high on the same factor. -->
+<!-- We removed items not consistently loading on one factor, -->
+<!-- and dropped secs_eco entirely. -->
+<!-- We applied these changes consistently across countries. -->
 
 ```{r, include=FALSE}
-use_scales <- lapply(scales_list, function(i){
-  thenames <- grepl("sepa_(soc|eco)", names(i))
-  if(any(thenames)){
-    i[which(thenames)] <- lapply(i[which(thenames)], `[`, 3:5)
-  }
-  i
-})
-use_scales <- lapply(use_scales, function(i){
-  thenames <- grepl("secs_soc", names(i))
-  if(any(thenames)){
-    i[which(thenames)] <- lapply(i[which(thenames)], `[`, 4:5)
-  }
-  i
-})
-use_scales$us$secs_eco <- NULL
+use_scales <- scales_list
 use_scales$nl$secs_eco <- NULL
+```
 
+```{r, eval = run_everything}
 set.seed(1)
@@
 })
+saveRDS(cfas, "cfas2.RData")
+saveRDS(meas_inv, "meas_inv.RData")
 ```
@@
 ```{r tabscaleuse, results = "asis"}
+cfas <- readRDS("cfas2.RData")
+meas_inv <- readRDS("meas_inv.RData")
 invisible(lapply(names(cfas), function(cntr){
@@
 
-```{r, code=xfun::read_utf8('../analysis.R')}
+```{r, eval = run_everything}
+library(worcs)
+library(lavaan)
+library(BFpack)
+library(ggplot2)
+library(tidySEM)
+library(metafor)
+set.seed(22)
+sample_sizes <- sapply(dat, nrow)
+hypotheses <- list("(fam_secs_soc_us, fam_secs_eco_us, fam_sepa_soc_dk, fam_sepa_eco_dk, fam_secs_soc_nl, fam_secs_eco_nl, fam_sepa_soc_nl, fam_sepa_eco_nl) > .1",
+                   "(grp_secs_soc_us, grp_secs_eco_us, grp_sepa_soc_dk, grp_sepa_eco_dk, grp_secs_soc_nl, grp_secs_eco_nl, grp_sepa_soc_nl, grp_sepa_eco_nl) > .1",
+                   "(rec_secs_soc_us, rec_secs_eco_us, rec_sepa_soc_dk, rec_sepa_eco_dk, rec_secs_soc_nl, rec_secs_eco_nl, rec_sepa_soc_nl, rec_sepa_eco_nl) > .1",
+                   "(her_secs_soc_us, her_secs_eco_us, her_sepa_soc_dk, her_sepa_eco_dk, her_secs_soc_nl, her_secs_eco_nl, her_sepa_soc_nl, her_sepa_eco_nl) > .1",
+                   "(def_secs_soc_us, def_secs_eco_us, def_sepa_soc_dk, def_sepa_eco_dk, def_secs_soc_nl, def_secs_eco_nl, def_sepa_soc_nl, def_sepa_eco_nl) > .1",
+                   "(fai_secs_soc_us, fai_secs_eco_us, fai_sepa_soc_dk, fai_sepa_eco_dk, fai_secs_soc_nl, fai_secs_eco_nl, fai_sepa_soc_nl, fai_sepa_eco_nl) < -.1",
+                   "(pro_secs_soc_us, pro_secs_eco_us, pro_sepa_soc_dk, pro_sepa_eco_dk, pro_secs_soc_nl, pro_secs_eco_nl, pro_sepa_soc_nl, pro_sepa_eco_nl) > .1"
+                   )
+hypotheses[[8]] <- gsub("[<>]", "=", gsub("\\b(fam|grp)_((sepa|secs)_(soc|eco))_", "\\2ON\\1_", gsub("\\) > 0 & \\(", ", ", paste0(gsub("-?\\.1", "0", hypotheses[[1]]), " & ", gsub(".1", "0", hypotheses[[2]], fixed = TRUE)))))
+hypotheses[[9]] <- gsub("fam", "rec", gsub("grp", "fai", hypotheses[[8]], fixed = TRUE), fixed = TRUE)
+
+mods_cor <- lapply(names(dat), function(country){
+  cntdat <- dat[[country]][unlist(use_scales[[country]])]
+  mod <- tidy_sem(cntdat)
+  measurement(mod)
+})
+names(mods_cor) <- names(dat)
+mods_8 <- lapply(mods_cor, function(x){
+  add_paths(x,   paste0((t(outer(paste0(unique(grep("^se", x$dictionary$scale, value = TRUE)), " ~ "),
+                                 unique(grep("^(fam|grp)", x$dictionary$scale, value = TRUE)), paste0))), collapse = "\n"))
+})
+mods_9 <- lapply(mods_cor, function(x){
+  add_paths(x,   paste0((t(outer(paste0(unique(grep("^se", x$dictionary$scale, value = TRUE)), " ~ "),
+                                 unique(grep("^(rec|fai)", x$dictionary$scale, value = TRUE)), paste0))), collapse = "\n"))
+})
+
+removeothercountries <- function(hyp, cnt){
+  gsub(",\\s+\\)", "\\)", gsub(paste0("\\b[a-zA-Z_]+(?<!", cnt, ")\\b,?"), "", hyp, perl = TRUE))
+}
+
+removeparameters <- function(hyp, est){
+  params_in_hyp <- bain:::params_in_hyp(hyp)
+  est <- names(est)
+  if(any(!params_in_hyp %in% est)){
+    for(param in params_in_hyp[!params_in_hyp %in% est]){
+      hyp <- gsub(paste0("\\b", param, "\\b,?"), "", hyp)
+    }
+    hyp <- gsub(",\\s+\\)", "\\)", hyp)
+    hyp <- gsub("\\(\\s+", "\\(", hyp)
+  }
+  hyp <- gsub("\\(([a-zA-Z_]+)\\)", "\\1", hyp)
+  if(length(bain:::params_in_hyp(hyp)) == 0) return(NA)
+  hyp
+}
+
+res_list <- lapply(mods_cor, function(x){estimate_lavaan(x)})
+res_list17 <- res_list
+res <- lapply(names(res_list), function(country){
+  thisfit = res_list[[country]]
+  tab <- bain:::lav_get_estimates(thisfit, standardize = TRUE, retain_which = "~~")
+  keep_these <- which(!grepl("~~(secs|sepa)_(soc|eco)$", names(tab$estimate)) & grepl("(secs|sepa)_(soc|eco)~~", names(tab$estimate)))
+  estimates <- tab$estimate[keep_these]
+  Sigma <- tab$Sigma[[1]][keep_these, keep_these]
+  names(estimates) <- paste0(gsub("~~", "_", names(estimates), fixed = TRUE), "_", country)
+  names(estimates) <- gsub("^(sepa|secs)_(.+?)_(.+?)_(.+)$", "\\3_\\1_\\2_\\4", names(estimates))
+  colnames(Sigma) <- rownames(Sigma) <- names(estimates)
+  list(est = estimates, sig = Sigma)
+})
+names(res) <- names(res_list)
+res_h17 <- res
+# Get individual BFs for each sample
+bf_individual <- sapply(1:length(res_list), function(i){
+  hyp <- paste2(unlist(
+    lapply(
+      lapply(hypotheses[1:7], removeothercountries, cnt = names(res_list)[i]),
+      removeparameters, est = res[[i]]$est)
+    ), collapse = "; ")
+  tmp <- BF(x = res[[i]]$est,
+            hypothesis = hyp,
+            Sigma = res[[i]]$sig,
+            n = sample_sizes[i])
+  tmp$BFtu_confirmatory[1:7]
+})
+out_cors <- apply(bf_individual, 1, prod)
+
+out_8 <- 
+  {
+    # fit model
+    res_list <- lapply(mods_8, function(x){estimate_lavaan(x)})
+    res_list8 <- res_list
+    res <- lapply(names(res_list), function(country){
+      thisfit = res_list[[country]]
+      tab <- bain:::lav_get_estimates(thisfit, standardize = TRUE, retain_which = "~")
+      estimates <- tab$estimate
+      Sigma <- tab$Sigma[[1]]
+      names(estimates) <- paste0(gsub("~", "ON", names(estimates), fixed = TRUE), "_", country)
+      colnames(Sigma) <- rownames(Sigma) <- names(estimates)
+      list(est = estimates, sig = Sigma)
+    })
+    res8 <- res
+    bf_individual8 <- sapply(1:length(res_list), function(i){
+      hyp <- removeparameters(removeothercountries(hypotheses[8], cnt = names(res_list)[i]), est = res[[i]]$est)
+      tmp <- BF(x = res[[i]]$est,
+                hypothesis = hyp,
+                Sigma = res[[i]]$sig,
+                n = sample_sizes[i])
+      tmp$BFtu_confirmatory[1]
+    })
+    prod(bf_individual8)
+  }
+out_9 <- 
+  {
+    # fit model
+    res_list <- lapply(mods_9, function(x){estimate_lavaan(x)})
+    res_list9 <- res_list
+    res <- lapply(names(res_list), function(country){
+      thisfit = res_list[[country]]
+      tab <- bain:::lav_get_estimates(thisfit, standardize = TRUE, retain_which = "~")
+      estimates <- tab$estimate
+      Sigma <- tab$Sigma[[1]]
+      names(estimates) <- paste0(gsub("~", "ON", names(estimates), fixed = TRUE), "_", country)
+      colnames(Sigma) <- rownames(Sigma) <- names(estimates)
+      list(est = estimates, sig = Sigma)
+    })
+    res9 <- res
+    bf_individual9 <- sapply(1:length(res_list), function(i){
+      hyp <- removeparameters(removeothercountries(hypotheses[9], cnt = names(res_list)[i]), est = res[[i]]$est)
+      tmp <- BF(x = res[[i]]$est,
+                hypothesis = hyp,
+                Sigma = res[[i]]$sig,
+                n = sample_sizes[i])
+      tmp$BFtu_confirmatory[1]
+    })
+    prod(bf_individual9)
+  }
+bayesfactors <- c(out_cors, 1/out_8, 1/out_9)
+est_for_hyp <- lapply(hypotheses, function(h){
+  pars = bain:::params_in_hyp(h)
+  tmp <- unlist(lapply(c(res_h17, res8, res9), function(i){
+    i$est[which(names(i$est) %in% pars)]
+  }))
+  nams <- names(tmp)
+  tmp <- data.frame(Value = tmp, Country = gsub("^.+(.{2})$", "\\1", nams), Parameter = gsub("^(.{2}\\.)?(.+?)_.{2}$", "\\2", nams))
+  tmp <- reshape(tmp, direction = "wide", idvar = "Country", timevar =  "Parameter")
+  rownames(tmp) <- NULL
+  names(tmp) <- gsub("Value\\.", "", names(tmp))
+  tmp
+})
+
+estimates <- lapply(names(res_list17), function(c){
+    x <- res_list17[[c]]
+    tmp <- standardizedSolution(x)
+    tmp <- tmp[tmp$op == "~~" & grepl("(soc|eco)", tmp$lhs) & !grepl("(soc|eco)", tmp$rhs), c("rhs", "lhs", "est.std", "se")]
+    names(tmp)[3] <- "ri"
+    tmp$social <- as.integer(grepl("_soc", tmp$lhs, fixed = TRUE))
+    tmp$eco <- as.integer(grepl("_eco", tmp$lhs, fixed = TRUE))
+    tmp$country <- c
+    tmp$ni <- unlist(x@Data@nobs)
+    tmp
+})
+estimates <- do.call(rbind, estimates)
+
+meta17 <- lapply(unique(estimates$rhs), function(x){
+  tmp <- estimates[estimates$rhs==x,]
+  tmp <- escalc(ri = tmp$ri, ni = tmp$ni, measure = "ZCOR", data = tmp)
+  # res <- rma(tmp$yi, vi = tmp$vi, mods = tmp[, c("social", "eco")], intercept = FALSE)
+  # if(length(unique(tmp$country))>2){
+  #   res <- robust(res, cluster = tmp$country)  
+  # }
+  tmp$id_study <- tmp$country
+  tmp$id_es <- 1:nrow(tmp)
+  res <- rma.mv(tmp$yi, tmp$vi, random = list(~ 1 | id_study, ~ 1 | id_es), data=tmp) 
+  confints <- confint(res)
+  tabres <- data.frame(Parameter = c(rownames(res$b), "Tau2b", "Tau2w"),
+                       Estimate = c(fisherz2r(res$b), res$sigma2),
+                       ci.lb = c(fisherz2r(res$ci.lb), confints[[1]]$random[1,2], confints[[2]]$random[1,2]),
+                       ci.ub = c(fisherz2r(res$ci.ub), confints[[1]]$random[1,3], confints[[2]]$random[1,3]),
+                       p = c(res$pval, NA, NA),
+                       sig = c(c("", "*")[(res$pval < .05)+1], c("", "*")[(c(confints[[1]]$random[1,2], confints[[2]]$random[1,2])> 1e-4)+1]),
+                       Model = "Overall")
+  # By conservatism dimension
+  res <- rma.mv(tmp$yi, tmp$vi, random = list(~ 1 | id_study, ~ 1 | id_es), data=tmp, intercept = FALSE, mods = tmp[, c("social", "eco")]) 
+  confints <- confint(res)
+  tabres2 <- data.frame(Parameter = c(rownames(res$b), "Tau2b", "Tau2w"),
+                       Estimate = c(fisherz2r(res$b), res$sigma2),
+                       ci.lb = c(fisherz2r(res$ci.lb), confints[[1]]$random[1,2], confints[[2]]$random[1,2]),
+                       ci.ub = c(fisherz2r(res$ci.ub), confints[[1]]$random[1,3], confints[[2]]$random[1,3]),
+                       p = c(res$pval, NA, NA),
+                       sig = c(c("", "*")[(res$pval < .05)+1], c("", "*")[(c(confints[[1]]$random[1,2], confints[[2]]$random[1,2])> 1e-4)+1]),
+                       Model = "Multigroup")
+  tabres <- rbind(tabres, tabres2)
+  tabres$CI <- conf_int(lb = tabres$ci.lb, ub = tabres$ci.ub)
+  tabres[c("ci.lb", "ci.ub")] <- NULL
+  tabres$Domain <- x
+  tabres
+})
+meta17 <- do.call(rbind, meta17)
+
+# Hypothesis 8 ------------------------------------------------------------
+source("mod89.R")
+res8 <- lapply(names(mod8), function(n){
+  sem(mod8[[n]], dat[[n]], auto.fix.first = FALSE, auto.var = TRUE, auto.cov.lv.x = TRUE, std.lv = TRUE, auto.cov.y = TRUE)
+})
+names(res8) <- names(mod8)
+
+estimates <- lapply(names(res8), function(c){
+  x <- res8[[c]]
+  tmp <- parameterestimates(x)
+  tmp <- tmp[!tmp$label == "", c("rhs", "lhs", "est", "se")]
+  names(tmp)[3] <- "bi"
+  tmp$social <- as.integer(grepl("_soc", tmp$lhs, fixed = TRUE))
+  tmp$eco <- as.integer(grepl("_eco", tmp$lhs, fixed = TRUE))
+  tmp$country <- c
+  tmp$ni <- unlist(x@Data@nobs)
+  tmp
+})
+estimates <- do.call(rbind, estimates)
+
+meta8 <- lapply(c("fam", "grp"), function(x){
+  tmp <- estimates[estimates$rhs==x,]
+  tmp$id_study <- tmp$country
+  tmp$id_es <- 1:nrow(tmp)
+  if(nrow(tmp) == 1) return(NULL)
+  res <- tryCatch({rma.mv(tmp$bi, tmp$se^2, random = list(~ 1 | id_study, ~ 1 | id_es), data=tmp) }, error = function(e){rma(tmp$bi, tmp$se^2, data=tmp)})
+  confints <- confint(res)
+  tabres <- data.frame(Parameter = c(rownames(res$b), "Tau2b", "Tau2w"),
+                       Estimate = c(fisherz2r(res$b), res$sigma2),
+                       ci.lb = c(fisherz2r(res$ci.lb), confints[[1]]$random[1,2], confints[[2]]$random[1,2]),
+                       ci.ub = c(fisherz2r(res$ci.ub), confints[[1]]$random[1,3], confints[[2]]$random[1,3]),
+                       p = c(res$pval, NA, NA),
+                       sig = c(c("", "*")[(res$pval < .05)+1], c("", "*")[(c(confints[[1]]$random[1,2], confints[[2]]$random[1,2])> 1e-4)+1]),
+                       Model = "Overall")
+  # By conservatism dimension
+  res <- try(rma.mv(tmp$bi, tmp$se^2, random = list(~ 1 | id_study, ~ 1 | id_es), data=tmp, intercept = FALSE, mods = tmp[, c("social", "eco")]))
+  if(inherits(res, "try-error")) return(tabres)
+  confints <- confint(res)
+  tabres2 <- data.frame(Parameter = c(rownames(res$b), "Tau2b", "Tau2w"),
+                        Estimate = c(fisherz2r(res$b), res$sigma2),
+                        ci.lb = c(fisherz2r(res$ci.lb), confints[[1]]$random[1,2], confints[[2]]$random[1,2]),
+                        ci.ub = c(fisherz2r(res$ci.ub), confints[[1]]$random[1,3], confints[[2]]$random[1,3]),
+                        p = c(res$pval, NA, NA),
+                        sig = c(c("", "*")[(res$pval < .05)+1], c("", "*")[(c(confints[[1]]$random[1,2], confints[[2]]$random[1,2])> 1e-4)+1]),
+                        Model = "Multigroup")
+  if(tabres$Estimate[1] == tabres2$Estimate[1]) return(tabres)
+  tabres <- rbind(tabres, tabres2)
+  tabres$CI <- conf_int(lb = tabres$ci.lb, ub = tabres$ci.ub)
+  tabres[c("ci.lb", "ci.ub")] <- NULL
+  tabres$Domain <- x
+  tabres
+})
+meta8 <- do.call(rbind, meta8)
+
+# Hypothesis 9 ------------------------------------------------------------
+
+res9 <- lapply(names(mod8), function(n){
+  mod <- mod8[[n]]
+  mod <- gsub("secs_soc_fam", "secs_soc_rec", mod, fixed = T)
+  mod <- gsub("secs_soc_grp", "secs_soc_fai", mod, fixed = T)
+  mod <- gsub("* fam", "* rec", mod, fixed = T)
+  mod <- gsub("* grp", "* fai", mod, fixed = T)
+  sem(mod, dat[[n]], auto.fix.first = FALSE, auto.var = TRUE, auto.cov.lv.x = TRUE, std.lv = TRUE, auto.cov.y = TRUE)
+})
+names(res9) <- names(mod8)
+
+estimates <- lapply(names(res9), function(c){
+  x <- res9[[c]]
+  tmp <- parameterestimates(x)
+  tmp <- tmp[!tmp$label == "", c("rhs", "lhs", "est", "se")]
+  names(tmp)[3] <- "bi"
+  tmp$social <- as.integer(grepl("_soc", tmp$lhs, fixed = TRUE))
+  tmp$eco <- as.integer(grepl("_eco", tmp$lhs, fixed = TRUE))
+  tmp$country <- c
+  tmp$ni <- unlist(x@Data@nobs)
+  tmp
+})
+estimates <- do.call(rbind, estimates)
+
+meta9 <- lapply(c("rec", "fai"), function(x){
+  tmp <- estimates[estimates$rhs==x,]
+  tmp$id_study <- tmp$country
+  tmp$id_es <- 1:nrow(tmp)
+  if(nrow(tmp) == 1) return(NULL)
+  res <- tryCatch({rma.mv(tmp$bi, tmp$se^2, random = list(~ 1 | id_study, ~ 1 | id_es), data=tmp) }, error = function(e){rma(tmp$bi, tmp$se^2, data=tmp)})
+  confints <- confint(res)
+  tabres <- data.frame(Parameter = c(rownames(res$b), "Tau2b", "Tau2w"),
+                       Estimate = c(fisherz2r(res$b), res$sigma2),
+                       ci.lb = c(fisherz2r(res$ci.lb), confints[[1]]$random[1,2], confints[[2]]$random[1,2]),
+                       ci.ub = c(fisherz2r(res$ci.ub), confints[[1]]$random[1,3], confints[[2]]$random[1,3]),
+                       p = c(res$pval, NA, NA),
+                       sig = c(c("", "*")[(res$pval < .05)+1], c("", "*")[(c(confints[[1]]$random[1,2], confints[[2]]$random[1,2])> 1e-4)+1]),
+                       Model = "Overall")
+  # By conservatism dimension
+  res <- try(rma.mv(tmp$bi, tmp$se^2, random = list(~ 1 | id_study, ~ 1 | id_es), data=tmp, intercept = FALSE, mods = tmp[, c("social", "eco")]))
+  if(inherits(res, "try-error")) return(tabres)
+  confints <- confint(res)
+  tabres2 <- data.frame(Parameter = c(rownames(res$b), "Tau2b", "Tau2w"),
+                        Estimate = c(fisherz2r(res$b), res$sigma2),
+                        ci.lb = c(fisherz2r(res$ci.lb), confints[[1]]$random[1,2], confints[[2]]$random[1,2]),
+                        ci.ub = c(fisherz2r(res$ci.ub), confints[[1]]$random[1,3], confints[[2]]$random[1,3]),
+                        p = c(res$pval, NA, NA),
+                        sig = c(c("", "*")[(res$pval < .05)+1], c("", "*")[(c(confints[[1]]$random[1,2], confints[[2]]$random[1,2])> 1e-4)+1]),
+                        Model = "Multigroup")
+  if(tabres$Estimate[1] == tabres2$Estimate[1]) return(tabres)
+  tabres <- rbind(tabres, tabres2)
+  tabres$CI <- conf_int(lb = tabres$ci.lb, ub = tabres$ci.ub)
+  tabres[c("ci.lb", "ci.ub")] <- NULL
+  tabres$Domain <- x
+  tabres
+})
+meta9 <- do.call(rbind, meta9)
+
+saveRDS(bayesfactors, "bayesfactors.RData")
+saveRDS(est_for_hyp, "est_for_hyp.RData")
+saveRDS(res_list17, "res_list17.RData")
+saveRDS(meta17, "meta17.RData")
+saveRDS(meta8, "meta8.RData")
+saveRDS(meta9, "meta9.RData")
 
@@
 
+First, we provide an overview of the latent variable correlations for each country.
+These are the model parameters evaluated using the informative hypothesis tests below:
+
+```{r templatecortabs, include=FALSE}
+res_list17 <- readRDS("res_list17.RData")
+out = NULL
+for (i in 1:length(res_list17)) {
+  out = c(out, knit_expand('template_tabcor.rmd'))
+}
+```
+
+`r paste(knit(text = out), collapse = '\n')`
+
+Next, we examine evidence for the preregistered hypotheses:
+
 ```{r tabresults, results = "asis"}
+bayesfactors <- readRDS("bayesfactors.RData")
+est_for_hyp <- readRDS("est_for_hyp.RData")
 interpret_bf <- function(bf){
@@
 
-```{r, include = FALSE, code=xfun::read_utf8('../analysis_tris.R')}
+```{r, eval = run_everything}
+library(worcs)
+library(lavaan)
+library(BFpack)
+library(ggplot2)
+library(tidySEM)
+tris <- load_data(to_envir = FALSE)[["tris"]]
 
+# Descriptives ------------------------------------------------------------
+scales_tris <-
+  lapply(unique(gsub("_\\d+$", "", names(tris))), function(i)
+    grep(i, names(tris), value = T))
+names(scales_tris) <- unique(gsub("_\\d+$", "", names(tris)))
+
+cfa_tris <- t(sapply(names(scales_tris), function(scal) {
+  scal <- paste0(scal, "_", 1:length(scales_tris[[scal]]))
+  out <-
+    cfa(paste0("F =~ ", paste0(scal, collapse = "+")), std.lv = TRUE, data = tris)
+  paran <- fa.parallel(tris[, scal])
+  tab <- table_results(out, columns = NULL, digits = 3)
+  tab <- tab[-nrow(tab),]
+  loadns <- as.numeric(tab$est_std)[tab$op == "=~"]
+  r2s <- lavInspect(out, "r2")
+  omga <- semTools::reliability(out, what = "omega")[1, 1]
+  c(
+    Subscale = gsub("_\\d$", "", scal[1]),
+    Items = length(scal),
+    n = out@Data@nobs[[1]],
+    formatC(unlist(table_fit(out)[1, c("chisq", "cfi", "tli", "rmsea", "srmr")]), digits = 3, format = "f"),
+    formatC(
+      c(
+        min_load = min(loadns),
+        max_load = max(loadns),
+        min_r2 = min(r2s),
+        max_r2 = max(r2s),
+        omega = omga
+      ),
+      digits = 3,
+      format = "f"
+    ),
+    Reliability = tidySEM:::interpret(omga),
+    Factors = paran$nfact
+  )
+}))
+
+sample_sizes <- nrow(tris)
+hypotheses <-
+  list(
+    "(fam_secs_soc_us, fam_secs_eco_us, fam_sepa_soc_dk, fam_sepa_eco_dk, fam_secs_soc_nl, fam_secs_eco_nl, fam_sepa_soc_nl, fam_sepa_eco_nl) > .1",
+    "(grp_secs_soc_us, grp_secs_eco_us, grp_sepa_soc_dk, grp_sepa_eco_dk, grp_secs_soc_nl, grp_secs_eco_nl, grp_sepa_soc_nl, grp_sepa_eco_nl) > .1",
+    "(rec_secs_soc_us, rec_secs_eco_us, rec_sepa_soc_dk, rec_sepa_eco_dk, rec_secs_soc_nl, rec_secs_eco_nl, rec_sepa_soc_nl, rec_sepa_eco_nl) > .1",
+    "(her_secs_soc_us, her_secs_eco_us, her_sepa_soc_dk, her_sepa_eco_dk, her_secs_soc_nl, her_secs_eco_nl, her_sepa_soc_nl, her_sepa_eco_nl) > .1",
+    "(def_secs_soc_us, def_secs_eco_us, def_sepa_soc_dk, def_sepa_eco_dk, def_secs_soc_nl, def_secs_eco_nl, def_sepa_soc_nl, def_sepa_eco_nl) > .1",
+    "(fai_secs_soc_us, fai_secs_eco_us, fai_sepa_soc_dk, fai_sepa_eco_dk, fai_secs_soc_nl, fai_secs_eco_nl, fai_sepa_soc_nl, fai_sepa_eco_nl) < -.1",
+    "(pro_secs_soc_us, pro_secs_eco_us, pro_sepa_soc_dk, pro_sepa_eco_dk, pro_secs_soc_nl, pro_secs_eco_nl, pro_sepa_soc_nl, pro_sepa_eco_nl) > .1"
+  )
+hypotheses[[8]] <-
+  gsub("[<>]",
+       "=",
+       gsub(
+         "\\b(fam|grp)_((sepa|secs)_(soc|eco))_",
+         "\\2ON\\1_",
+         gsub("\\) > 0 & \\(", ", ", paste0(
+           gsub("-?\\.1", "0", hypotheses[[1]]),
+           " & ",
+           gsub(".1", "0", hypotheses[[2]], fixed = TRUE)
+         ))
+       ))
+hypotheses[[9]] <-
+  gsub("fam",
+       "rec",
+       gsub("grp", "fai", hypotheses[[8]], fixed = TRUE),
+       fixed = TRUE)
+
+mod <- tidy_sem(tris)
+mod_cor <- measurement(mod)
+
+mod_8 <-
+  add_paths(mod_cor, paste0((t(
+    outer(paste0(unique(
+      grep("^se", mod_cor$dictionary$scale, value = TRUE)
+    ), " ~ "),
+    unique(
+      grep("^(fam|grp)", mod_cor$dictionary$scale, value = TRUE)
+    ), paste0)
+  )), collapse = "\n"))
+
+mod_9 <-
+  add_paths(mod_cor,   paste0((t(
+    outer(paste0(unique(
+      grep("^se", mod_cor$dictionary$scale, value = TRUE)
+    ), " ~ "),
+    unique(
+      grep("^(rec|fai)", mod_cor$dictionary$scale, value = TRUE)
+    ), paste0)
+  )), collapse = "\n"))
+
+removeothercountries <- function(hyp, cnt) {
+  gsub(",\\s+\\)", "\\)", gsub(paste0("\\b[a-zA-Z_]+(?<!", cnt, ")\\b,?"), "", hyp, perl = TRUE))
+}
+
+removeparameters <- function(hyp, est) {
+  params_in_hyp <- bain:::params_in_hyp(hyp)
+  est <- names(est)
+  if (any(!params_in_hyp %in% est)) {
+    for (param in params_in_hyp[!params_in_hyp %in% est]) {
+      hyp <- gsub(paste0("\\b", param, "\\b,?"), "", hyp)
+    }
+    hyp <- gsub(",\\s+\\)", "\\)", hyp)
+    hyp <- gsub("\\(\\s+", "\\(", hyp)
+  }
+  hyp <- gsub("\\(([a-zA-Z_]+)\\)", "\\1", hyp)
+  if (length(bain:::params_in_hyp(hyp)) == 0)
+    return(NA)
+  hyp
+}
+
+res17 <- estimate_lavaan(mod_cor)
+res_tris <- res17
+tab <-
+  bain:::lav_get_estimates(res17, standardize = TRUE, retain_which = "~~")
+keep_these <-
+  which(
+    !grepl("~~(secs|sepa)_(soc|eco)$", names(tab$estimate)) &
+      grepl("(secs|sepa)_(soc|eco)~~", names(tab$estimate))
+  )
+estimates <- tab$estimate[keep_these]
+Sigma <- tab$Sigma[[1]][keep_these, keep_these]
+names(estimates) <-
+  gsub("~~", "_", names(estimates), fixed = TRUE)
+names(estimates) <-
+  gsub("^(sepa|secs)_(.+?)_(.+?)$", "\\3_\\1_\\2", names(estimates))
+colnames(Sigma) <- rownames(Sigma) <- names(estimates)
+res <- list(est = estimates, sig = Sigma)
+res17 <- res
+# Get BF
+hyp <- paste2(unlist(lapply(
+  gsub("_us", "", lapply(hypotheses[1:7], removeothercountries, cnt = "us")),
+  removeparameters, est = res$est
+)), collapse = "; ")
+tmp <- BF(
+  x = res$est,
+  hypothesis = hyp,
+  Sigma = res$sig,
+  n = sample_sizes
+)
+
+out_cors <- tmp$BFtu_confirmatory[1:7]
+
+out_8 <-
+  {
+    # fit model
+    res <- estimate_lavaan(mod_8)
+    res <- {
+      thisfit = res
+      tab <-
+        bain:::lav_get_estimates(thisfit, standardize = TRUE, retain_which = "~")
+      estimates <- tab$estimate
+      Sigma <- tab$Sigma[[1]]
+      names(estimates) <-
+        gsub("~", "ON", names(estimates), fixed = TRUE)
+      colnames(Sigma) <- rownames(Sigma) <- names(estimates)
+      list(est = estimates, sig = Sigma)
+    }
+    res_tris8 <- res
+
+    hyp <- paste2(removeparameters(gsub(
+      "_us",
+      "",
+      lapply(hypotheses[8], removeothercountries, cnt = "us")
+    ),
+    est = res$est))
+    tmp <- BF(
+      x = res$est,
+      hypothesis = hyp,
+      Sigma = res$sig,
+      n = sample_sizes
+    )
+    tmp$BFtu_confirmatory[1]
+
+  }
+out_9 <-
+  {
+    # fit model
+    res <- estimate_lavaan(mod_9)
+    res <- {
+      thisfit = res
+      tab <-
+        bain:::lav_get_estimates(thisfit, standardize = TRUE, retain_which = "~")
+      estimates <- tab$estimate
+      Sigma <- tab$Sigma[[1]]
+      names(estimates) <-
+        gsub("~", "ON", names(estimates), fixed = TRUE)
+      colnames(Sigma) <- rownames(Sigma) <- names(estimates)
+      list(est = estimates, sig = Sigma)
+    }
+    res_tris9 <- res
+
+    hyp <- paste2(removeparameters(gsub(
+      "_us",
+      "",
+      lapply(hypotheses[9], removeothercountries, cnt = "us")
+    ),
+    est = res$est))
+    tmp <- BF(
+      x = res$est,
+      hypothesis = hyp,
+      Sigma = res$sig,
+      n = sample_sizes
+    )
+    tmp$BFtu_confirmatory[1]
+
+  }
+
+bayesfactors_tris <- c(out_cors, 1 / out_8, 1 / out_9)
+est_for_hyp_tris <- lapply(hypotheses, function(h) {
+  pars = gsub("_us", "", bain:::params_in_hyp(h))
+  tmp <- unlist(lapply(list(res17, res_tris8, res_tris9), function(i) {
+    tryCatch(i$est[which(names(i$est) %in% pars)], error = function(e){ NA })
+  }))
+  tmp
+})
+
+saveRDS(bayesfactors_tris, "bayesfactors_tris.RData")
+saveRDS(est_for_hyp_tris, "est_for_hyp_tris.RData")
+saveRDS(res_tris, "res_tris.RData")
+```
+
+```{r}
+bayesfactors_tris <- readRDS("bayesfactors_tris.RData")
+est_for_hyp_tris <- readRDS("est_for_hyp_tris.RData")
+res_tris <- readRDS("res_tris.RData")
 ```
@@
 The fit of this model was also poor, though somewhat better than for the confirmatory analyses; `r paste0(names(trisfit), " = ", formatC(trisfit, digits = 3, format = "f"), collapse = ", ")`.
+
+# Meta-analyses
+
+Whereas the preregistered hypotheses test the hypothesis that *all* correlations between *all* moral domains and *all* conservatism scales will be > .1 in *all* countries,
+we can also examine the *average* correlation between moral domains and conservatism scales across countries.
+
+For this purpose, we conducted three-level meta-analyses.
+We estimated two separate models for each moral domain:
+One with an average correlation (intercept) across all conservatism scales (Model: Overall),
+and one multi-group analysis with separate intercepts for social and economic conservatism scales (Model: Multigroup).
+To account for the dependent data, we used a three-level meta-analysis.
+Note that each model provides an estimate of variance between effect sizes within each country (tau$^2$w) and variance between the countries (tau$^2$b).
+
+```{r, results = "asis"}
+meta17 <- readRDS("meta17.RData")
+kbl(meta17, caption = "Average correlations according to three-level meta-analysis", digits = 3) |>
+  kable_styling(bootstrap_options = c("striped", "hover"))
+```
+
+For Hypotheses 8 and 9, it is instructive to examine the average partial regression coefficients for the two moral domains mentioned in the hypotheses:
+
+```{r meta8, results = "asis"}
+meta8 <- readRDS("meta8.RData")
+kbl(meta8, caption = "Average partial regression coefficients according to three-level meta-analysis", digits = 3) |>
+  kable_styling(bootstrap_options = c("striped", "hover"))
+```
+
+```{r meta9, results = "asis"}
+meta9 <- readRDS("meta9.RData")
+kbl(meta9, caption = "Average partial regression coefficients according to three-level meta-analysis", digits = 3) |>
+  kable_styling(bootstrap_options = c("striped", "hover"))
+```

### 2021-12-16 analysis.R

@@ -3,7 +3,9 @@ library(lavaan)
 library(BFpack)
 library(ggplot2)
 library(tidySEM)
+library(metafor)
 set.seed(22)
+dat <- load_data(to_envir = FALSE)[1:3]
 sample_sizes <- sapply(dat, nrow)
 hypotheses <- list("(fam_secs_soc_us, fam_secs_eco_us, fam_sepa_soc_dk, fam_sepa_eco_dk, fam_secs_soc_nl, fam_secs_eco_nl, fam_sepa_soc_nl, fam_sepa_eco_nl) > .1",
                    "(grp_secs_soc_us, grp_secs_eco_us, grp_sepa_soc_dk, grp_sepa_eco_dk, grp_secs_soc_nl, grp_secs_eco_nl, grp_sepa_soc_nl, grp_sepa_eco_nl) > .1",
@@ -145,3 +147,173 @@ est_for_hyp <- lapply(hypotheses, function(h){
   tmp
 })
 
+estimates <- lapply(names(res_list17), function(c){
+    x <- res_list17[[c]]
+    tmp <- standardizedSolution(x)
+    tmp <- tmp[tmp$op == "~~" & grepl("(soc|eco)", tmp$lhs) & !grepl("(soc|eco)", tmp$rhs), c("rhs", "lhs", "est.std", "se")]
+    names(tmp)[3] <- "ri"
+    tmp$social <- as.integer(grepl("_soc", tmp$lhs, fixed = TRUE))
+    tmp$eco <- as.integer(grepl("_eco", tmp$lhs, fixed = TRUE))
+    tmp$country <- c
+    tmp$ni <- unlist(x@Data@nobs)
+    tmp
+})
+estimates <- do.call(rbind, estimates)
+
+meta17 <- lapply(unique(estimates$rhs), function(x){
+  tmp <- estimates[estimates$rhs==x,]
+  tmp <- escalc(ri = tmp$ri, ni = tmp$ni, measure = "ZCOR", data = tmp)
+  # res <- rma(tmp$yi, vi = tmp$vi, mods = tmp[, c("social", "eco")], intercept = FALSE)
+  # if(length(unique(tmp$country))>2){
+  #   res <- robust(res, cluster = tmp$country)  
+  # }
+  tmp$id_study <- tmp$country
+  tmp$id_es <- 1:nrow(tmp)
[…]

### 2021-12-16 analysis_tris.R

@@ -212,6 +212,7 @@ out_9 <-
     tmp$BFtu_confirmatory[1]
     
   }
+
 bayesfactors_tris <- c(out_cors, 1 / out_8, 1 / out_9)
 est_for_hyp_tris <- lapply(hypotheses, function(h) {
   pars = gsub("_us", "", bain:::params_in_hyp(h))
@@ -220,3 +221,7 @@ est_for_hyp_tris <- lapply(hypotheses, function(h) {
   }))
   tmp
 })
+
+saveRDS(bayesfactors_tris, "bayesfactors_tris.RData")
+saveRDS(est_for_hyp_tris, "est_for_hyp_tris.RData")
+saveRDS(res_tris, "res_tris.RData")

### 2021-12-16 manuscript/mod89.R

@@ -1,0 +1,117 @@
+mod8 <- list(nl = "sepa_soc =~ sepa_soc_1
+sepa_soc =~ sepa_soc_2
+sepa_soc =~ sepa_soc_3
+sepa_soc =~ sepa_soc_4
+sepa_soc =~ sepa_soc_5
+sepa_eco =~ sepa_eco_1
+sepa_eco =~ sepa_eco_2
+sepa_eco =~ sepa_eco_3
+sepa_eco =~ sepa_eco_4
+sepa_eco =~ sepa_eco_5
+secs_soc =~ secs_soc_1
+secs_soc =~ secs_soc_2
+secs_soc =~ secs_soc_3
+secs_soc =~ secs_soc_4
+secs_soc =~ secs_soc_5
+secs_soc =~ secs_soc_6
+secs_soc =~ secs_soc_7
+fam =~ fam_1
+fam =~ fam_2
+fam =~ fam_3
+grp =~ grp_1
+grp =~ grp_2
+grp =~ grp_3
+rec =~ rec_1
+rec =~ rec_2
+rec =~ rec_3
+def =~ def_1
+def =~ def_2
+def =~ def_3
+fai =~ fai_1
+fai =~ fai_2
+fai =~ fai_3
+pro =~ pro_1
+pro =~ pro_2
+pro =~ pro_3
+sepa_soc ~ sepa_soc_fam * fam
+sepa_soc ~ sepa_soc_grp * grp
+sepa_eco ~ sepa_eco_fam * fam
+sepa_eco ~ sepa_eco_grp * grp
+secs_soc ~ secs_soc_fam * fam
+secs_soc ~ secs_soc_grp * grp
+d_secs_soc := secs_soc_fam-secs_soc_grp",
+dk =
+"sepa_soc =~ sepa_soc_1
+sepa_soc =~ sepa_soc_2
+sepa_soc =~ sepa_soc_3
+sepa_soc =~ sepa_soc_4
+sepa_soc =~ sepa_soc_5
+sepa_eco =~ sepa_eco_1
+sepa_eco =~ sepa_eco_2
+sepa_eco =~ sepa_eco_3
+sepa_eco =~ sepa_eco_4
+sepa_eco =~ sepa_eco_5
+fam =~ fam_1
+fam =~ fam_2
+fam =~ fam_3
+grp =~ grp_1
+grp =~ grp_2
+grp =~ grp_3
+rec =~ rec_1
+rec =~ rec_2
+rec =~ rec_3
+her =~ her_1
[…]

### 2022-10-05 manuscript/manuscript.Rmd
update 2022-10-05 07:56:44

@@
 library("worcs")
-run_everything = FALSE
+run_everything = TRUE
 knitr::opts_chunk$set(echo = FALSE, results = "hide", message = FALSE, warning = FALSE)
@@
 res_list <- lapply(mods_cor, function(x){estimate_lavaan(x)})
+# simdat <- lapply(1:3, function(i) simulateData(parTable(res_list[[i]]), sample.nobs = sample_sizes[i]))
+# for(i in 1:3){
+#   worcs::add_synthetic(simdat[[i]], original_name = paste0(names(mods_cor)[i], ".csv"), worcs_directory = "../")
+# }
 res_list17 <- res_list
@@
 library(tidySEM)
-tris <- load_data(to_envir = FALSE)[["tris"]]
+tris <- load_data(to_envir = FALSE, worcs_directory = "../")[["tris"]]
 
@@
 res17 <- estimate_lavaan(mod_cor)
+#simdat <- simulateData(parTable(res17), sample.nobs = nrow(tris))
+#worcs::add_synthetic(simdat, original_name = "tris.csv", worcs_directory = "../")
+
 res_tris <- res17

### 2022-10-05 prepare_data.R

@@ -36,8 +36,10 @@ dk[rev_these] <- mapply(function(c, vec){c-vec}, c = maxval, vec = dk[rev_these]
 closed_data(dk, synthetic = FALSE)
 
 us <- read.csv("us_original.csv", stringsAsFactors = FALSE, skip = 2, header = FALSE)
-names_us <- read.csv("us_original.csv", stringsAsFactors = FALSE)
-names(us) <- tolower(names(names_us))
+names_us <- readLines("us_original.csv", n = 1)
+names_us <- strsplit(names_us, ",")[[1]]
+names_us <- tolower(names_us)
+names(us) <- names_us
 all(unlist(scales_list$us) %in% names(us))
 us <- us[unlist(scales_list$us)]
 names(us) <- unlist(lapply(names(scales_list$us), function(nam){paste0(nam, "_", 1:length(scales_list$us[[nam]]))}))
@@ -68,3 +70,11 @@ tris[rev_these] <- mapply(function(c, vec){c-vec}, c = maxval, vec = tris[rev_th
 
 names(tris) <- unlist(lapply(names(scales_tris), function(i){paste0(i, "_", 1:length(scales_tris[[i]]))}))
 closed_data(tris, synthetic = FALSE)
+
+dats <- list(dk = dk, nl = nl, us = us, tris = tris)
+for(n in names(dats)){
+  tmp <- tidySEM::tidy_sem(dats[[n]])
+  tmp <- tidySEM::create_scales(tmp)
+  write.csv(tmp$descriptives, file = paste0("descriptives_", n, ".csv"), row.names = FALSE)
+  write.csv(tmp$correlations, file = paste0("correlations_", n, ".csv"), row.names = FALSE)
+}
